ITHIM

### 2021-10-20 latex/output-md.Rmd
Add references

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+

@@

+:==========================================+=================================================================+:===================================+================================+================+
| Name                                      | Description                                                     | Value in Accra model               | Label                          | Model/ Setting |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+
| \$\\epsilon \$                            | Walk time to bus                                                | 5 or Lnorm(log (5),0.18)           | BUS\_ WALK_TIME                | Setting        |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+
| $\mu_{m=HGV}$ \|                          | Truck distance relative to car \|                               | 0.21 or Beta(3,10)                 | TRUCK_TO\_ CAR_RATIO \| S      | etting         |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+
| $\mu_{m=bus}$ \|                          | Bus driver distance relative to bus passenger distance \|       | 1/45 or Bet a(20,600) \|           | BUS\_ TO_PASSEN GER_RATIO      | Setting        |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+
| $\eta$                                    | Background PM2.5 concentration                                  | 50 or Lnorm(log( 50),0.18) \|      | PM_CONC_BASE \|                | Setting        |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+
| $\zeta$                                   | Fraction of measured PM2.5 concentration due to road transport  | 0.225 or Beta(5,20) \|             | PM_TRANS_SHARE \|              | Setting        |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+
| $P$                                       | Vehicle emission confidence                                     | 1                                  | EM ISSION_INVENTORY_CONFIDENCE | Setting        |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+
| $C_1$                                     | Base-level inhalation rate                                      | 1                                  | BAS E_LEVEL_I NHALATION \_RATE | Model          |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+
| $C_2$                                     | Exposure ratio window closed                                    | 0.5                                | CLOSED_WI NDOW_PM\_ RATIO      | Model          |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+
| $\chi$                                    | Day-to-week travel scalar                                       | 7 or 7 $\times$Beta(20,3)          | DAY_TO_WEEK \_TRAVEL_SCALAR    | Model          |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+--------------------------------+----------------+

@@

\[Example of the dose--response workflow for PA and total cancer. Top left: results of the metaanalysis: mean, lower bound and upper bound of the relationship between PA dose and relative risk of disease. Top right: examples of 500 samples from the normal distribution defined by the mean of the top-left panel and the standard deviation defined by (upper bound minus lower bound) divided by 1.96 and truncated at 0. Bottom left: relative risks of individuals with PA doses 5, 25 and 45 are found by mapping their doses onto the median curve. This is used in the "constant" ITHIM use case. Bottom right: relative risks of individuals with PA doses 5, 25 and 45 for three different samples from the distribution shown in the top-right panel. For each sample, each individual is mapped onto the response curve it defines.\]

@@

| \$ \che ck{T}\_{a,g,m,s}=\frac{\bar{T}_{a,                                                                                                                   | Relative travel per mode and scenario by age and gender                                        | inj_distan ces\[\[1\]\]                      |

@@

| $\tilde{T}_{m,s}=\frac{\hat{T}_{ m, s}}{\hat{T}_{m,s=\text{baseline}}}$                                                                                      | Total travel per mode and scenario relative to baseline, with car modes summed, and Tuktuk = 1 | inj_distan ces\[\[2\]\]                      |

@@

| $\dot{P}_{m}=\left\{\begin{array}{lr} \gam ma_m & P=1 \\ \tilde{\gamma}_m, \  | tilde{\gamma}_m \sim \text{Dir}(f(P,\  | gamma_m)) & P<1 \end{array}\right.$ | Emissions by mode \| \|                                                                        | tra ns_emissions                             |

@@

| $\tilde{P}_{m,s}=\dot{P}_m\hat{T} _{ m,s}/\hat{T}_{m,s=\text{baseline}}$                                                                                     | Emissions by mode in scenario relative to baseline                                             | tra ns_emissions                             |

@@

| $K_s=C_4-C_5\log(\bar{P_s})$                                                                                                                                 | On-road PM2.5 exposure ratio                                                                   | on_road_of f_road_ratio                      |

@@

| $\tilde{K}_{m\                                                                                                                                               | On-road PM2.5 exposure ratio for open vehicle                                                  | on_road_of f_road_ratio                      |

@@

| $\                                                                                                                                                           | In-vehicle PM2.5 exposure ratio                                                                | in_v ehicle_ratio                            |

@@

| $\bar{U}_{a,g,h,o}=U_{a ,g ,h,o}\frac{\bar{N}_{a,g}}{N_{a,g}}$                                                                                               | GBD scaled to local population                                                                 | DI SEASE_BURDEN                              |

@@

| $\tilde{U}_{a, g, h,o}=\rho_h\cdot \bar{U}_{a,g,h,o}$                                                                                                        | Scaled background disease for Neoplasms, IHD, Lung cancer                                      | gbd \_data_scaled                            |

>>>>

bibliography: ithim.bib

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+:==========================================+=================================================================+:===================================+===============================+====================+
| **Name**                                  | **Description**                                                 | **Value in Accra model**           | **Label**                     | **Model/ Setting** |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| \$\\epsilon \$                            | Walk time to bus                                                | 5 or Lnorm(log (5),0.18)           | BUS_WALK_TIME                 | Setting            |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\mu_{m=HGV}$                             | Truck distance relative to car                                  | 0.21 or Beta(3,10)                 | TRUCK_TO\_ CAR_RATIO          | Setting            |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\mu_{m=bus}$                             | Bus driver distance relative to bus passenger distance          | 1/45 or Bet a(20,600) \|           | BUS_TO_PASSENGER_RATIO        | Setting            |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\eta$                                    | Background PM2.5 concentration                                  | 50 or Lnorm(log( 50),0.18) \|      | PM_CONC_BASE                  | Setting            |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\zeta$                                   | Fraction of measured PM2.5 concentration due to road transport  | 0.225 or Beta(5,20) \|             | PM_TRANS_SHARE                | Setting            |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $P$                                       | Vehicle emission confidence                                     | 1                                  | EMISSION_INVENTORY_CONFIDENCE | Setting            |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $C_1$                                     | Base-level inhalation rate                                      | 1                                  | BASE_LEVEL_INHALATION_RATE    | Model              |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $C_2$                                     | Exposure ratio window closed                                    | 0.5                                | CLOSED_WINDOW_PM\_ RATIO      | Model              |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+
| $\chi$                                    | Day-to-week travel scalar                                       | 7 or 7 $\times$Beta(20,3)          | DAY_TO_WEEK_TRAVEL_SCALAR     | Model              |
+-------------------------------------------+-----------------------------------------------------------------+------------------------------------+-------------------------------+--------------------+

@@

\[Example of the dose--response workflow for PA and total cancer. Top left: results of the meta-analysis: mean, lower bound and upper bound of the relationship between PA dose and relative risk of disease. Top right: examples of 500 samples from the normal distribution defined by the mean of the top-left panel and the standard deviation defined by (upper bound minus lower bound) divided by 1.96 and truncated at 0. Bottom left: relative risks of individuals with PA doses 5, 25 and 45 are found by mapping their doses onto the median curve. This is used in the "constant" ITHIM use case. Bottom right: relative risks of individuals with PA doses 5, 25 and 45 for three different samples from the distribution shown in the top-right panel. For each sample, each individual is mapped onto the response curve it defines.\]

@@

| \$ \che ck{T}\_{a,g,m,s}=\frac{\bar{T}_{a,                                                                                                                   | Relative travel per mode and scenario by age and gender                                        | inj_distances\[\[1\]\]                       |

@@

| $\tilde{T}_{m,s}=\frac{\hat{T}_{ m, s}}{\hat{T}_{m,s=\text{baseline}}}$                                                                                      | Total travel per mode and scenario relative to baseline, with car modes summed, and Tuktuk = 1 | inj_distances\[\[2\]\]                       |

@@

| $\dot{P}_{m}=\left\{\begin{array}{lr} \gam ma_m & P=1 \\ \tilde{\gamma}_m, \  | tilde{\gamma}_m \sim \text{Dir}(f(P,\  | gamma_m)) & P<1 \end{array}\right.$ | Emissions by mode \| \|                                                                        | trans_emissions                              |

@@

| $\tilde{P}_{m,s}=\dot{P}_m\hat{T} _{ m,s}/\hat{T}_{m,s=\text{baseline}}$                                                                                     | Emissions by mode in scenario relative to baseline                                             | trans_emissions                              |

@@

| $K_s=C_4-C_5\log(\bar{P_s})$                                                                                                                                 | On-road PM2.5 exposure ratio                                                                   | on_road_off_road_ratio                       |

@@

| $\tilde{K}_{m\                                                                                                                                               | On-road PM2.5 exposure ratio for open vehicle                                                  | on_road_off_road_ratio                       |

@@

| $\                                                                                                                                                           | In-vehicle PM2.5 exposure ratio                                                                | in_vehicle_ratio                             |

@@

| $\bar{U}_{a,g,h,o}=U_{a ,g ,h,o}\frac{\bar{N}_{a,g}}{N_{a,g}}$                                                                                               | GBD scaled to local population                                                                 | DISEASE_BURDEN                               |

@@

| $\tilde{U}_{a, g, h,o}=\rho_h\cdot \bar{U}_{a,g,h,o}$                                                                                                        | Scaled background disease for Neoplasms, IHD, Lung cancer                                      | gbd_data_scaled                              |
